### 2022-06-16 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@e57162f06f949bbb2947b87ea8c1580e70b187be 🚀

Despite the difference in evolutionary distinctiveness globally, there
are reasons to expect that the phylogeography of bats and
betacoronaviruses should show some degree of congruence. High density of
hosts sharing the same virus (albeit possibly different strains) can
drive or result from evolution of the bat antiviral immune system,
resulting in spatially distinct immunological responses, as evidenced in
several bat species (Banerjee et al. 2020). Immune characteristics that
allow bats to be better adapted to infection by emerging viruses
(Gorbunova et al., 2020; Irving et al., 2021), in addition to being
hardcoded in their genome (\textbf{Jebb et al.~six\ldots{}}), may be
related to a wide variety of diets (Jones et al., 2022; Moreno Santillán
et al., 2021; Banerjee et al., 2020; Schneeberger et al., 2013; Muylaert
et al., 2021), themselves likely to be driven by spatial effects,
especially at the local scale -- bats, indeed, occupy a variety of
environments, and therefore display a variety of adaptations to these
environments.

@@

@@

@@

@@

@@

>>>>

Despite the difference in evolutionary distinctiveness globally, there
are reasons to expect that the phylogeography of bats and
betacoronaviruses should show some degree of congruence. High density of
hosts sharing the same virus (albeit possibly different strains) can
drive or result from evolution of the bat antiviral immune system,
resulting in spatially distinct immunological responses, as evidenced in
several bat species (Banerjee et al. 2020). Immune characteristics that
allow bats to be better adapted to infection by emerging viruses
(Gorbunova et al. 2020, Irving et al. 2021), in addition to being
hardcoded in their genome (Jebb et al. 2020), may be related to a wide
variety of diets (Banerjee et al. 2020, Moreno Santillán et al. 2021,
Muylaert et al. 2021), themselves likely to be driven by spatial
effects, especially at the local scale -- bats, indeed, occupy a variety
of environments, and therefore display a variety of adaptations to these
environments.

@@

\leavevmode\hypertarget{ref-Gorbunova2020WorGoe}{}%
Gorbunova, V. et al. 2020. The World Goes Bats: Living Longer and
Tolerating Viruses. - Cell Metabolism 32: 31--43.

@@

\leavevmode\hypertarget{ref-Irving2021LesHos}{}%
Irving, A. T. et al. 2021. Lessons from the host defences of bats, a
unique viral reservoir. - Nature 589: 363--370.

@@

\leavevmode\hypertarget{ref-Jebb2020SixRef}{}%
Jebb, D. et al. 2020. Six reference-quality genomes reveal evolution of
bat adaptations. - Nature 583: 578--584.

@@

\leavevmode\hypertarget{ref-MorenoSantillan2021LarGen}{}%
Moreno Santillán, D. D. et al. 2021. Large-scale genome sampling reveals
unique immunity and metabolic adaptations in bats. - Molecular Ecology:
mec.16027.

@@

\leavevmode\hypertarget{ref-Muylaert2021PreFut}{}%
Muylaert, R. L. et al. 2021. Present and future distribution of bat
hosts of sarbecoviruses: Implications for conservation and public
health.
